---
title: "Round 1 Sandbox and Notes for Updates"
author: "Dan Johnson"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Progress Report

1.	Need to clarify where/how best to provide a shared site.
Problem I have is that I am using confidential data in private repo. Should I:

* Document activities in the Default website space.
* Pull data and munge in a private repo folder to create public dataset, then call in the de-identified data only?

2.  Where do you want us to conduct the actual analyses? In: 

* Default website repo
*	A repo with Mike's data-specific file and folder structure
* Other location?

3.	How deep do you want us to go on documenting process?

*	All raw work?
*	Notes and scribbles in .rmd
*	Train of thought journals?

4.  I have specific R coding questions in Round_1_Data_intake_method.Rmd.


## R Sandbox

.r
source(".")



Model for Pipelines

Name of file format: Pipeline_NameOfProcess_ver#.r

Build with source(".") files
  Each calls a piece of a larger process.
  
  
Use .gitignore to set what does NOT get moved to GitHub

https://help.github.com/articles/ignoring-files/

https://git-scm.com/docs/gitignore



Rio
https://github.com/leeper/rio


Amazon Redshift

Use R Plumber to build API for database access.
https://www.rplumber.io/


Use mutate and row_number to create TA and studnt name substitutions, then  join to combine and anonymize.

Classify the texts I have already using Naive Bayes

Book: Teacher Written Commentary
Lynn Goldstein

https://www.press.umich.edu/6737/teacher_written_commentary_in_second_language_writing_classrooms


  




  
  
```{text}

aes <- 
  readtext(file = "plain_texts/*.txt", # read each file .txt
           docvarsfrom = "filenames", # get attributes from filename
           docvarnames = c("language", "country", "year", "title", "type", "genre", "imdb_id")) # add the column names we want for each attribute

glimpse(aes) # preview structure of the object
```


```{r}
library(tidytext)
library(readtext)
```



```{r}
text_files_list <- readtext(file = "plain_texts/*.txt")
```

