---
title: "Round 1 Sandbox and Notes for Updates"
author: "Dan Johnson"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Progress Report

1.	Need to clarify where/how best to provide a shared site.
Problem I have is that I am using confidential data in private repo. Should I:

* Document activities in the Default website space.
* Pull data and munge in a private repo folder to create public dataset, then call in the de-identified data only?

2.  Where do you want us to conduct the actual analyses? In: 

* Default website repo
*	A repo with Mike's data-specific file and folder structure
* Other location?

3.	How deep do you want us to go on documenting process?

*	All raw work?
*	Notes and scribbles in .rmd
*	Train of thought journals?

4.  I have specific R coding questions in Round_1_Data_intake_method.Rmd.


## R Sandbox

Development plan should be to build the workflow using Jerid's "pipeline" template. 

Model for a pipeline is to have a standard file name format like:

Pipeline_NameOfProcess_ver#.r

It calls scripts directly using ```source("xxx.r")``` lines.  

This resembles how I am working already, building individual steps as blocks that can be assembled and organized many ways.

Think of the documentation of a pipeline as saying where each block begins and ends. What are its inputs, outputs?


Build with source(".") files
  Each calls a piece of a larger process.
  
Keeping Confidentiality  
  Use .gitignore to set what does NOT get moved to GitHub
    https://help.github.com/articles/ignoring-files/
    https://git-scm.com/docs/gitignore



##Using Rio for data input

  https://rdrr.io/cran/rio/man/import.html

  https://riptutorial.com/r/example/1580/importing-data-with-rio

  https://github.com/leeper/rio


##Tools

http://www.unit-conversion.info/texttools/random-string-generator/

A random alphanumeric generator. Took 3 seconds to generate 10,000 non-repeating 8-character strings to use for random IDs.


##Modifications to Data Tables Names, Added Data Files

**scrap_names.csv** is a dummy file for testing join methods

**TA_and_Student_IDs.csv** is the file that maps student emails and TA names to their unique ID numbers. If I can keep it behind privacy wall, the dataset will be de-identifiable using ID values only.

In main dataset:
```
Added "unique.record". Set each semester, adds unique ID for each comment record. Format is Sp18.00001, Sp18.00002,...

  Modified column names:
    report.id
						sort (can drop)
    report.title
						student (Still need to de-identify)
    course
						ta (Still need to de-identify)
    lab
						tag (Student enters, but is potentially incorrect)
    type.TA
    grade.TA
    grading.time
						Rank (can drop)

    hypothesis.ok
    data.ok
    citation.ok
    interpretation.ok
    organization.ok
    techflaws.ok
    writing.ok
    comments.incorporated

    ta.comment

    code.subject
    code.structure
    code.locus
    code.scope
    code.tone
    code.notes
```




http://www.sthda.com/english/wiki/tidyr-crucial-step-reshaping-data-with-r-for-easier-analyses

gather()
Collapse multiple columns into key-value pairs. Collapse columns into rows.

spread()
Separate a set of key-value pairs into multiple columns. Spread rows into columns.



separate()
Separate one column into several at a defined character

unite()
Unite multiple columns into one using some kind of character to connect. Think connecting words in columns using "\_" to write snake\_case.


https://r4ds.had.co.nz/tidy-data.html



gather(data, key, value, ...)
	Data is the data frame
	Key, value are names of the two columns being used to create output.
	... specifies columns to gather. 
	
```
my_data2 <- gather(my_data,
                   key = "arrest_attribute",
                   value = "arrest_estimate",
                   -state)
my_data2
```
Sorry but key-value pairs is not making sense to me. 
	Is it that k/v pairs are not the strict two-part data structures I am thinking about from RDS, and more a way to think bout the data as it moves? Is the alternative way to think about it that first column is coming from the table header (key) and appropriate value for that row comes along? If so, then we can predict that for every data line, the anchor will be replicated one time for each key column.
	YES, the variable NAMES are what is referred to as the key column.



There are three interrelated rules which make a dataset tidy:
```
    Each variable must have its own column.
    Each observation must have its own row.
    Each value must have its own cell.
```

Use JOIN to take two separate tables of data and combine them. Use GATHER to reorganize existing data.


complete() takes a set of columns, and finds all unique combinations. It then ensures the original dataset contains all those values, filling in explicit NAs where necessary.

There’s one other important tool that you should know for working with missing values. Sometimes when a data source has primarily been used for data entry, missing values indicate that the previous value should be carried forward:

treatment <- tribble(
  ~ person,           ~ treatment, ~response,
  "Derrick Whitmore", 1,           7,
  NA,                 2,           10,
  NA,                 3,           9,
  "Katherine Burke",  1,           4
)

You can fill in these missing values with fill(). It takes a set of columns where you want missing values to be replaced by the most recent non-missing value (sometimes called last observation carried forward).





Amazon Redshift

Use R Plumber to build API for database access.
https://www.rplumber.io/


Use mutate and row_number to create TA and studnt name substitutions, then  join to combine and anonymize.

Classify the texts I have already using Naive Bayes

Book: Teacher Written Commentary
Lynn Goldstein

https://www.press.umich.edu/6737/teacher_written_commentary_in_second_language_writing_classrooms


  




  
  
```{text}

aes <- 
  readtext(file = "plain_texts/*.txt", # read each file .txt
           docvarsfrom = "filenames", # get attributes from filename
           docvarnames = c("language", "country", "year", "title", "type", "genre", "imdb_id")) # add the column names we want for each attribute

glimpse(aes) # preview structure of the object
```


```{r}
library(tidytext)
library(readtext)
```



```{r}
text_files_list <- readtext(file = "plain_texts/*.txt")
```

