---
title: "Sandbox"
author: "Dan Johnson"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Progress Report

1.	Need to clarify where/how best to provide a shared site.
Problem I have is that I am using confidential data in private repo. Should I:

* Document activities in the Default website space.
* Pull data and munge in a private repo folder to create public dataset, then call in the de-identified data only?

2.  Where do you want us to conduct the actual analyses? In: 

* Default website repo
*	A repo with Mike's data-specific file and folder structure
* Other location?

3.	How deep do you want us to go on documenting process?

*	All raw work?
*	Notes and scribbles in .rmd
*	Train of thought journals?

4.  I have questions in Data_intake_1.Rmd.


## R Sandbox

```{r text}

aes <- 
  readtext(file = "plain_texts/*.txt", # read each file .txt
           docvarsfrom = "filenames", # get attributes from filename
           docvarnames = c("language", "country", "year", "title", "type", "genre", "imdb_id")) # add the column names we want for each attribute

glimpse(aes) # preview structure of the object
```


```{r}
library(tidytext)
library(readtext)
```



```{r}
text_files_list <- readtext(file = "plain_texts/*.txt")
```

